---
title: "EXPD: Kickstarter Dataset Analysis"
author: "Christian Bosshard & Enea David Fedel"
date: "2024-12-19"
output:
    html_notebook:
        toc: true
        toc_float: true
        code_folding: "hide"
        highlight: pygments
bibliography: ../assets/references.bib
---

<style>
    .main-container {
        max-width: 1400px;
        margin: 0 auto;
    }
</style>

# Introduction

In this paper, we take a closer look at data from the crowdfunding platform `Kickstarter`. Launched in 2009, Kickstarter was one of the first to create a space where innovators could share their ideas and get funding from supporters all over the world. Today, it’s the top player in this growing market.

We analyzed recent data to see how this new way of funding is doing and what makes a project successful in getting support from the community.

# The Dataset

The dataset we're going to look at can be found [here](https://www.kaggle.com/datasets/ulrikthygepedersen/kickstarter-projects). It contains comprehensive data of over 300'000 Kickstarter projects, ranging from 2009 (founding year) until 2018. Let's take a closer look:

```{r class.source = 'fold-show'}
kickstarter <- read.csv("../data/kickstarter_projects.csv", encoding = "UTF-8")
str(kickstarter)
```

Each row represents one project, which means it contains exactly 374'853 projects with the following variables:

| Variable name | Type                  | Description                                                           |
|---------------|-----------------------|-----------------------------------------------------------------------|
| ID            | numeric - discrete    | The ID of a given project                                             |
| Name          | categorical - nominal | The name of a given project                                           |
| Category      | categorical - nominal | The category of a given project                                       |
| Subcategory   | categorical - nominal | The subcategory of a given project                                    |
| Country       | categorical - nominal | The country the project was launched from                             |
| Launched      | numeric - discrete    | The date the project was first open for funding                       |
| Deadline      | numeric - discrete    | The date by when the project needs to reach it's funding goal         |
| Goal          | numeric - discrete    | The amount of US dollars needed to successfully fund the project      |
| Pledged       | numeric - discrete    | How much money in US dollars people have already commited the project |
| Backers       | numeric - discrete    | How many people have / are supporting a project                       |
| State         | categorical - ordinal | The state of a project, depends on if it reaches it's goal amount     |

# Data Exploration

## Univariate Visualizations

To get a better understanding of the dataset, we created two univariate visualizations to analyze the distribution of categories and countries. These visualizations provide important context for interpreting the bi- and multivariate analyses later on.

<br>

```{r, child=c('vis1.Rmd')}
```

<br>

```{r, child=c('vis2.Rmd')}
```

<br>

## Bi- and Multivariate Visualizations

For the bi- and multivariate visualizations, we analyze various KPIs (Key Performance Indicators) to better understand what makes a Kickstarter project successful and to identify what strategies work — or no longer work.

<br>

```{r, child=c('vis3.Rmd')}
```

<br>

```{r, child=c('vis4.Rmd')}
```

<br>

```{r, child=c('vis5.Rmd')}
```

<br>

```{r, child=c('vis6.Rmd')}
```

<br>

# Summary

<br><br>

# References

<div id="refs"></div>
