---
title: "Visualization 4"
output: html_document
---

### Success rate by category

<script type="text/javascript">
function showSolution(){
    first=document.getElementById('first')
    second=document.getElementById('second')
    if(first.style.visibility=='visible'){
        first.style.visibility='hidden';
        first.style.display='none';
        second.style.visibility="visible";
        second.style.display='block';
    }else{
        first.style.visibility="visible";
        first.style.display='block';
        second.style.visibility='hidden';
        second.style.display='none';
    }
}
</script>

To understand what works and what doesn’t, we calculated a "success rate" by averaging the number of successful projects within each category and coloring the bars based on the mean goal for that category.

<div id='first' style='visibility:visible;display:block'>

```{r, fig.width = 10, fig.height = 6, message = FALSE, warning = FALSE, tidy = 'styler'}
library(dplyr)
library(ggplot2)

kickstarter.success.category <- kickstarter %>%
  group_by(Category) %>%
  summarize(success_rate = mean(State == "Successful", na.rm = TRUE),
    mean_goal = mean(Goal, na.rm = TRUE)
  )

ggplot(kickstarter.success.category, aes(x = reorder(Category, success_rate), y = success_rate, fill = mean_goal)) +
geom_col() +
scale_y_continuous(labels = scales::percent) +
scale_fill_viridis_c(name = "Mean Goal   ", option = "plasma") +
labs(title = "Success rate by category\nwith mean goal amount",
x = "Category",
y = "Success Rate") +
theme_minimal(base_size = 18) +
theme(axis.text.x = element_text(angle = 45, hjust = 1)
)

```

</div>
<div id='second' style='visibility:hidden;display:none'>

```{r, fig.width = 10, fig.height = 6, message = FALSE, warning = FALSE, tidy = 'styler'}
kickstarter.success.category <- kickstarter %>%
  group_by(Category) %>%
  summarize(success_rate = mean(State == "Successful", na.rm = TRUE),
            median_goal = median(Goal, na.rm = TRUE)
  )

ggplot(kickstarter.success.category, aes(x = reorder(Category, success_rate), y = success_rate, fill = median_goal)) +
geom_col() +
scale_y_continuous(labels = scales::percent) +
scale_fill_viridis_c(name = "Median Goal", option = "plasma") +
labs(title = "Success rate by category\nwith median goal amount",
x = "Category",
y = "Success Rate") +
theme_minimal(base_size = 18) +
theme(axis.text.x = element_text(angle = 45, hjust = 1)
)
```

</div>

We anticipated an inverse correlation, where higher goals would correspond to lower success rates, but the correlation turned out to be weak. For instance, while Technology has the lowest success rate at 20% and the highest mean goal, other categories don’t follow as clear a pattern.

An interesting outlier is the category "Film & Video". While its success rate is roughly average, it has a noticeably higher mean goal compared to neighboring categories. We interpret this as a reflection of the high costs often associated with producing movies or TV shows. This likely results in a significant number of outliers with exceptionally high goals, which skew the mean upward.

But what if we calculate goal with median? Press the button to change it to the median: <button type='button' class="btn btn-primary" onclick='showSolution();'>Change plot</button>

Ah! As we can see "Film & Video" is now much more in line with its neighbours. Interestingly Technology is still the top category in terms of goal amount.

Of course to properly find out the outliers in each category one could make a boxplot, but that is left as an exercise to the reader!
