---
title: "Visualization 4"
output: html_document
---

# Visualization 4

<script type="text/javascript">
function showSolution(){
    first=document.getElementById('first')
    second=document.getElementById('second')
    if(first.style.visibility=='visible'){
        first.style.visibility='hidden';
        first.style.display='none';
        second.style.visibility="visible";
        second.style.display='block';
    }else{
        first.style.visibility="visible";
        first.style.display='block';
        second.style.visibility='hidden';
        second.style.display='none';
    }
}
</script>

And for our last plot we have a bit of a complex one. We calculated a "success rate" by getting the average amount of successful projects by category and colored the bars by the mean goal of that category. We were hoping for a inverse correlation, but it's rather weak. While Technology is the lowest category with a success rate of 20% and the highest mean goal, everything else isn't as clear of a correlation.
<br>
One interesting outlier is the category "Film & Video": While being around the middle in terms of success rate it has a remarkably higher mean goal than its neighbours. Our interpretation of that is that Movies or TV Shows can get very expensive, so there may be a considerable amount of outliers with high goals in that category, which would screw with the mean:

<div id='first' style='visibility:visible;display:block'>
```{r, fig.width = 10, fig.height = 6, message = FALSE, warning = FALSE, tidy = 'styler'}
library(dplyr)
library(ggplot2)

kickstarter.success.category <- kickstarter %>%
  group_by(Category) %>%
  summarize(success_rate = mean(State == "Successful", na.rm = TRUE),
    mean_goal = mean(Goal, na.rm = TRUE)
  )

ggplot(kickstarter.success.category, aes(x = reorder(Category, success_rate), y = success_rate, fill = mean_goal)) +
geom_col() +
scale_y_continuous(labels = scales::percent) +
scale_fill_viridis_c(name = "Mean Goal   ", option = "plasma") +
labs(title = "Success rate by category\nwith mean goal amount",
x = "Category",
y = "Success Rate") +
theme_minimal(base_size = 18) +
theme(axis.text.x = element_text(angle = 45, hjust = 1)
)

```
</div>

<div id='second' style='visibility:hidden;display:none'>
```{r, fig.width = 10, fig.height = 6, message = FALSE, warning = FALSE, tidy = 'styler'}
kickstarter.success.category <- kickstarter %>%
  group_by(Category) %>%
  summarize(success_rate = mean(State == "Successful", na.rm = TRUE),
            median_goal = median(Goal, na.rm = TRUE)
  )

ggplot(kickstarter.success.category, aes(x = reorder(Category, success_rate), y = success_rate, fill = median_goal)) +
geom_col() +
scale_y_continuous(labels = scales::percent) +
scale_fill_viridis_c(name = "Median Goal", option = "plasma") +
labs(title = "Success rate by category\nwith median goal amount",
x = "Category",
y = "Success Rate") +
theme_minimal(base_size = 18) +
theme(axis.text.x = element_text(angle = 45, hjust = 1)
)
```
</div>

But what if calculate goal with median? Press the below button to change it to median:<br>
<button type='button' class="btn btn-primary" onclick='showSolution();'>Change plot</button><br>
Ah! As we can see "Film & Video" is now much more in line with its neighbours. Interestingly Technology is still the top category in terms of goal amount.
<br><br>
Of course to properly find out the outliers in each category one could make a boxplot, but that is an exercise left up to the reader!

